Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-02-16 submission/cv_models.tex
v1.4

\begin{figure}[t]
    \centering
    \subfigure[Log Frobenius Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_lognorm_accs.png}
        %KDD% \includegraphics[width=4.0cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    %KDD% 
    \qquad
    \subfigure[Log Spectral Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        %KDD% \includegraphics[width=4.0cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    %KDD% 
    \qquad
    \subfigure[ Weighted Alpha, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        %KDD% \includegraphics[width=4.0cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    %KDD% 
    \qquad
    \subfigure[Log $\alpha$-Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        %KDD% \includegraphics[width=4.0cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of Average Log Norm and Weighted Alpha quality metrics versus reported test accuracy for pretrained VGG models (with and without BN), trained on ImageNet, available in pyTorch (v1.x).  Metrics fit by linear regression, RMSE reported. }
    \label{fig:vgg-metrics}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \subfigure[Log Frobenius Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_lognorm_accs.png}
        %KDD% \includegraphics[width=4.0cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    %KDD% 
    \qquad
    \subfigure[Log Spectral Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        %KDD% \includegraphics[width=4.0cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    %KDD% 
    \qquad
    \subfigure[ Weighted Alpha, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        %KDD% \includegraphics[width=4.0cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    %KDD% 
    \qquad
    \subfigure[Log $\alpha$-Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        %KDD% \includegraphics[width=4.0cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of Average Log Norm and Weighted Alpha quality metrics versus reported test accuracy for pretrained VGG models (with and without BN), trained on ImageNet, available in pyTorch (v1.4).  Metrics fit by linear regression, RMSE reported. }
    \label{fig:vgg-metrics}
\end{figure}
